Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.8)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-28 results.tex
Added description of models

The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

In order to provide more detailed information \blue{that will be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. Also no additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.

>>>>

The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations made from a hybrid quark-diquark model with a Regge term that is included to accurately describe parton distribution functions at low $x$ values. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.

The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005). The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain. The presented data is well described by the calculations.

In order to provide more detailed information \blue{that can be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. Also no additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.
